---
title: "cl1"
author: "Lacapra Daniele"
date: "12 giugno 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(GA)
```
 PATH FRA CLUSTER
 ```{r}
setwd("C:\\Users\\danie\\Desktop\\Decision Models\\Progetto")
```

```{r}
library(GA)
cl1 <- read.csv("cluster1.csv")
cl1 <- cl1[,3:4]
(cl1)

set.seed(1324)
cluster1 <- kmeans(cl1, 20)
#faccio i 20 sotto-cluster nel cluster 1

cl1$cluster=as.factor(cluster1$cluster)
Cluster1 <- as.matrix(cluster1$centers)
Cluster1
head(cl1)
distance <- dist(Cluster1, method = "euclidean", diag = FALSE, upper = FALSE, p = 2)

set.seed(1234)


tourLength <- function(tour, distMatrix) {
  route <- embed(tour, 2)[, 2:1]
  sum(distMatrix[route])
}
# inverse of the total distance is the fitness
tpsFitness <- function(tour, ...) {
  1/tourLength(tour, ...)
}



GA.fit <- ga(type = "permutation", 
             fitness = tpsFitness, 
             distMatrix = distance, 
             min   = 1, 
             max = attr(distance, "Size"), 
             popSize = 200, 
             maxiter = 1000, 
             run = 100, 
             pmutation = 0.2,
             keepBest = TRUE)

```


```{r}
summary(GA.fit)
GA.fit@solution
tour <- GA.fit@solution[1, ]
```
```{r}
mds <- cmdscale(distance)
x <- mds[, 1]
y <- -mds[, 2]
# n <- length(x)
plot(x, y, type = "n", asp = 1, xlab = "", ylab = "", main = "Tour after GA converged")
points(x, y, pch = 16, cex = 1.5, col = "grey")
abline(h = pretty(range(x), 10), 
       v = pretty(range(y), 10), 
       col = "lightgrey")
tour <- GA.fit@solution[1, ]
tour <- c(tour, tour[1])
n <- length(tour)
arrows(x[tour[-n]], 
       y[tour[-n]], 
       x[tour[-1]], 
       y[tour[-1]], 
       length = 0.10, 
       angle = 45, 
       col = "red", 
       lwd = 1)
text(x, y - 100, labels(distance), cex = 0.8)

x[tour[-n]]
```

PATH ENTRO I CLUSTER

```{r}
setwd("C:\\Users\\danie\\Desktop\\Decision Models\\Progetto\\cluster1")
cl1 <- read.csv("cluster1.csv")
cl1 <- cl1[,3:4]

tourLength <- function(tour, distMatrix) {
  tour <- c(tour, tour[1])
  route <- embed(tour, 2)[, 2:1]
  sum(distMatrix[route])
}
# inverse of the total distance is the fitness
tpsFitness <- function(tour, ...) {
  1/tourLength(tour, ...)
}

set.seed(1324)
cluster1 <- kmeans(cl1, 20)
#faccio i 20 sotto-cluster nel cluster 1
cl1$cluster=as.factor(cluster1$cluster)
Cluster1 <- as.matrix(cluster1$centers)


vett <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)
for (i in vett) {
  temp <- subset(cl1, cluster == i)
  file <- as.character(paste("cl1_", i, ".csv", sep="")) 
  a <- assign(file, temp)
  a <- data.frame(a)
  write.csv(a, file)
  }

```



```{r}
vett <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)
length_1 <- list()

for (i in vett){
  file <- as.character(paste("cl1_", i, ".csv", sep=""))
  cl1_ <- read.csv(file)
  cl1_ <- cl1_[,2:3]
  distance <- dist(cl1_, method = "euclidean", diag = FALSE, upper = FALSE, p = 2)

  GA.fit <- ga(type = "permutation", 
             fitness = tpsFitness, 
             distMatrix = distance, 
             min   = 1, 
             max = attr(distance, "Size"), 
             popSize = 50, 
             maxiter = 5000, 
             run = 100, 
             pmutation = 0.2,
             keepBest = TRUE)
  length_1[[i]] <- min(apply(GA.fit@solution, 1, tourLength, distance))
}

cl1
```

```{r}
distance_within_cluster <- list()
length_1
distance_within_cluster[[1]] <- Reduce("+", GA.fit@solution[1,])
distance_within_cluster
length_1
Reduce("+", GA.fit@solution[1,])
GA.fit@solution
dim(GA.fit@solution)
```

```{r}
mds <- cmdscale(distance)
x <- mds[, 1]
y <- -mds[, 2]
# n <- length(x)
plot(x, y, type = "n", asp = 1, xlab = "", ylab = "", main = "Tour after GA converged")
points(x, y, pch = 16, cex = 1.5, col = "grey")
abline(h = pretty(range(x), 10), 
       v = pretty(range(y), 10), 
       col = "lightgrey")

tour <- GA.fit@solution[1, ]
tour <- c(tour, tour[1])
n <- length(tour)
arrows(x[tour[-n]], 
       y[tour[-n]], 
       x[tour[-1]], 
       y[tour[-1]], 
       length = 0.10, 
       angle = 45, 
       col = "steelblue", 
       lwd = 1)
text(x, y - 100, row.names(cl1_), cex = 0.8)
n <- length(tour)
lines(x[tour[-n]], y[tour[-n]], col = "red", lwd = 1)
```

```{r}
solution <- GA.fit@solution
row.names(solution) <- paste0("nrow",i)
solution <- data.frame(t(solution))
solution[,paste0("position",i)] <- row.names(solution)
row.names(solution) <- 1:nrow(solution)
solution <- merge(solution, cl1_, 
                    by.x = paste0("nrow",i), by.y = paste0("nrow"))
colnames(solution) <- c("nrow", "position","nrow2", "id", "x","y", "cluster", "nrow3")
percorso <- rbind(percorso, solution["id"])
```
```{r}
temp1 <- sol
file <- as.character(paste("sol", i, ".csv", sep="")) 
a <- assign(file, temp1)
a <- data.frame(a)
write.csv(a, file)
```

CENTROIDI DEI 10 CLASTER

```{r}
cl1 <- read.csv("cluster1.csv")
x_cl1 <- mean(Cluster1[,1]) 
y_cl1 <- mean(Cluster1[,2])
cl1_mean <- cbind(x_cl1, y_cl1)
x_cl2 <- mean(Cluster2[,1])
y_cl2 <- mean(Cluster2[,2])
cl2_mean <- cbind(x_cl2, y_cl2)
cl2_mean
cl_tot <- rbind(cl1_mean, cl2_mean)
cl_tot
x_cl3 <- mean(Cluster3[,1]) 
y_cl3 <- mean(Cluster3[,2])
cl3_mean <- cbind(x_cl3, y_cl3)
cl_tot <- rbind(cl_tot, cl3_mean)
x_cl4 <- mean(Cluster4[,1]) 
y_cl4 <- mean(Cluster4[,2])
cl4_mean <- cbind(x_cl4, y_cl4)
cl_tot <- rbind(cl_tot, cl4_mean)
cl_tot
x_cl5 <- mean(Cluster5[,1]) 
y_cl5 <- mean(Cluster5[,2])
cl5_mean <- cbind(x_cl5, y_cl5)
cl_tot <- rbind(cl_tot, cl5_mean)
x_cl6 <- mean(Cluster6[,1]) 
y_cl6 <- mean(Cluster6[,2])
cl6_mean <- cbind(x_cl6, y_cl6)
cl_tot <- rbind(cl_tot, cl6_mean)
x_cl7 <- mean(Cluster7[,1]) 
y_cl7 <- mean(Cluster7[,2])
cl7_mean <- cbind(x_cl7, y_cl7)
cl_tot <- rbind(cl_tot, cl7_mean)
x_cl8 <- mean(Cluster8[,1]) 
y_cl8 <- mean(Cluster8[,2])
cl8_mean <- cbind(x_cl8, y_cl8)
cl_tot <- rbind(cl_tot, cl8_mean)
x_cl9 <- mean(Cluster9[,1]) 
y_cl9 <- mean(Cluster9[,2])
cl9_mean <- cbind(x_cl9, y_cl9)
cl_tot <- rbind(cl_tot, cl9_mean)
x_cl10 <- mean(Cluster10[,1]) 
y_cl10 <- mean(Cluster10[,2])
cl10_mean <- cbind(x_cl10, y_cl10)
cl_tot <- rbind(cl_tot, cl10_mean)
cl_tot
```

```{r}
cl_tot <- as.matrix(cl_tot)
colnames(cl_tot) <- c("x", "y")
row.names(cl_tot) <-c(1,2,3,4,5,6,7,8,9,10)
cl_tot
```
```{r}
distance <- dist(cl_tot, method = "euclidean", diag = FALSE, upper = FALSE, p = 2)
distance
```

```{r}
set.seed(1234)
GA.fit <- ga(type = "permutation", 
             fitness = tpsFitness, 
             distMatrix = distance, 
             min   = 1, 
             max = attr(distance, "Size"), 
             popSize = 200, 
             maxiter = 1000, 
             run = 100, 
             pmutation = 0.2,
             keepBest = TRUE)


```

```{r}
mds <- cmdscale(distance)
x <- mds[, 1]
y <- -mds[, 2]
# n <- length(x)
plot(x, y, type = "n", asp = 1, xlab = "", ylab = "", main = "Tour after GA converged")
points(x, y, pch = 16, cex = 1.5, col = "grey")
abline(h = pretty(range(x), 10), 
       v = pretty(range(y), 10), 
       col = "lightgrey")

tour <- GA.fit@solution[1, ]
tour <- c(tour, tour[1])
n <- length(tour)
arrows(x[tour[-n]], 
       y[tour[-n]], 
       x[tour[-1]], 
       y[tour[-1]], 
       length = 0.10, 
       angle = 45, 
       col = "steelblue", 
       lwd = 1)
text(x, y - 100, row.names(cl_tot), cex = 0.8)
x[tour[-1]]
```

myEuclid <- function(points1, points2) {
    distanceMatrix <- matrix(NA, nrow=dim(points1)[1], ncol=dim(points2)[1])
    for(i in 1:nrow(points2)) {
        distanceMatrix[,i] <- sqrt(rowSums(t(t(points1)-points2[i,])^2))
    }
    distanceMatrix
}

UNIONE SOLUZIONI
```{r}
setwd("C:\\Users\\danie\\Desktop\\Decision Models\\Progetto\\cluster6")
percorso_ottimo <- data.frame(ncol=3)
colnames(percorso_ottimo) <- "id"
vett <- c(6,4,7,10,14,17,18,20,2,1,5,8,12,19,16,11,13,9,15,3)
for (i in vett){
  file <- as.character(paste("sol", i, ".csv", sep=""))
  sol <- read.csv(file)
  percorso_ottimo <- append(percorso_ottimo, sol$id)
  percorso_ottimo <- data.frame(matrix(unlist(percorso_ottimo), byrow=T))
  colnames(percorso_ottimo)<- "id"
}
percorso_ottimo

